Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies

### 2016-07-13 ms.tex
Paper now repopulated by thesis draft and with all final edits in place for Thesis Submissions; Cuts must be made (h277?)

@@

Using cosmological hydrodynamic simulations of Milky Way-type Galaxies, we explore the effect of accreted gas as feeding mechanisms for supermassive black holes. We examine two of these galaxies with differing merger histories using the Gasoline N-body+SPH code. One of there galaxies is characterized by several major mergers and the other with a quiescent history. We attempt to identify the importance of merger history on black hole accretion. Additionally, we consider a second, higher resolution version of the Milky Way-type galaxy with an active merger history using the Charm N-body GrAvity solver, ChaNGa.  This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes. Bellovary found that the gas accreted by the central black holes was proportional to that accreted by the host galaxy. Contrary to the previous study's results, we've found that while a galaxy with a quiescent history will still have a SMBH whose accretion mirrors that of its host, a galaxy with an active merger history has a central black hole that is preferentially fueled by gas accreted through mergers. Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history. Our results imply that galaxy mergers play an important role in the feeding of the SMBHs in the class of Milky Way-type galaxies.

\end{abstract}

\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others?}

@@

%[Note to self: Cite one canonical person but also more junior people in the field.]

%\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
 %\S\ref{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies. \citep{Kormendy2013} In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence. \citep{Alexander2005,Papovich2006,Volonteri2012} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together. \citep[5-8 citations here]{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects. \citep{Ferrarese2000} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. % For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e. less massive SMBH reside in galaxies with less disperse bulges, and more massive SMBH live in galaxies with larger velocity dispersions in their bulges. 
The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass. \citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside. \citep{VanDenBosch2007,Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation. \citep{Micic2007,Volonteri2009,Reines2013,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges. \citep{DiMatteo2005,Shen2008} Major mergers are thought to supply gas to the central SMBH resutling in feedback which quenches star formation and affects the structure of the galaxy.

@@

% For thesis: M-sigma plot:
\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines). Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
\label{msigma} 
\end{figure}
% Cite: Xiao

% For thesis: Explain feedback:
%Black hole feedback: the reaction effect of the energy obtained through gas accretion, which affects the overarching structure of the host galaxy.

% FOR SHOCKS: The simulations I am studying are run with a new implementation of Gasoline, which models hydrodynamic processes like shocks very well by using a geometric density average in the SPH force expression

The black hole mass-bulge luminosity relation was first implied by the work of \cite{Dressler1988}. \cite{Dressler1989} first proposed the correlation and it was first illustrated by \cite{Kormendy1993}. 
%The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.  
A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the currect, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides. \citep{Richards2006,Reddy2008,Hopkins2010} Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred. \citep{Treister2012} Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.

In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.  \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}[Maybe a different Ellison paper?] It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers. \citep[Which 1990's Tremaine?]{Springel2005,Kocevski2011} Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich. More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}. 
Smooth accretion, in particular, may play an important role in fueling these low mass galaxies. Halos less than 10$^{11} M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo. \citep{Keres2005} Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy. \citep{Brooks2007,Dekel2009,Nelson2013} Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs. \citep{Kormendy2013}

It is clear that galaxy hosts grow through variety of channels that depend on mass, environment, and interaction history. Therefore, we want to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself. \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH. Using a similar method as \cite{Bellovary2013}, this work compares the SMBH and galaxy fueling mechanisms between two Milky Way (MW) mass galaxies.

We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories. Our ``active'' galaxy, h258 \ref{h258face}, has a history characterized by major mergers, while our ``quiet'' galaxy, h277 \ref{h277face}, has a quiescent history with only minor mergers. Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them. We will compare the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within these galaxies. %Along these lines, we will also discuss the fueling mechanisms which vary between these galaxies of similar mass due to different merger and formation histories. 
MW-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.  By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine which accretion methods dominate in this class of galaxies.

%Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]

% ##########################################################
% ########################################################## 
% ########################################################## 
\section{Simulation Parameters}\label{sec-model}

[NOTE TO SELF: Make/include merger trees. Ask Christina?]

The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep[][Stadel 2001, how do I cite a PhD thesis?]{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.

An initial DM-only, uniform resolution 50 comoving Mpc box determined which halos would be selected for zoom-in examination, including the two halos examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively. The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively. A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z $\sim$ 3. A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution. Both simulations were run from z=150 to z=0.  [Make sure this is true for low res. True for high res.]

Gas can reach a minimum temperature of $\sim$100 K, without the inclusion of cooling via molecular hydrogen or metals. The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must remain below a temperature threshold of 10$^4$ K. Star particles form along the Kroupa initial mass function \citep{Kroupa2001}. Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the method of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant. SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method. Both supernova ``blastwave'' radius calculations and supernova (Ia and II) prescriptions are as described in detail by \cite{Stinson2006}. A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}. Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. These parameter and resolution choices allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation. \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH. We exclude AGN feedback in these small to moderate mass galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.

Since, there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent the theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants\citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}. While this method allows the BH formation process to remain physically motivated. BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity. \citep{Stinson2006} A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3. \citep{Volonteri2008} 
%This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.  
BH seed formation ends at z $\sim$ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. BH formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. \citep[Change citations?]{Bellovary2010,Zolotov2012}

Black hole mergers occur when they are separated by less than twice the softening length, and must be bound or satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via merger, black holes gain mass through Bondi-Hoyle gas accretion:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}
where $\alpha$ is a constant equal to 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas. Feedback is applied to the surrounding gas as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively. This energy is distributed as thermal energy to the 32 nearest particles via a kernal probability function. Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008} We find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations. However, as our main concern is in the relative proportion of gas in various phases, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.

@@

Our low resolution simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.  [Include starting numbers of gas, DM, and stars?] Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications. \cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy. This code includes a force resolution of 260 comoving pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $9 \times 10^4 M_{\odot}$.

[NOTE TO SELF: Combine sub sections? This one is too short?]

%FOR THESIS ONLY: [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]

@@

We used Charm N-body GrAvity solver, ChaNGa, a high resolution version of the same volume. The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: metal line cooling \citep{Christensen2012,Shen2010}, gas-phase and dust grain H$_2$ formation \citep{Christensen2014}, star formation dependence on H$_2$, and H$_2$ destruction from Lyman-Werner radiation. Other changes include a spline force softening lengths of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$. Star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$. Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total. The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.  At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.

In this paper, we demonstrate that the results from this high resolution ChaNGa simulation has results which confirm those found by the low resolution Gasoline version of the same galaxy simulation. This secondary analysis allows us to feel confident in our results as we describe the varying origins of fueling gas accreting onto the simulated Milky Way-mass galaxy, h258.

@@

% ##########################################################
% ##########################################################	
% ##########################################################
\section{Reduction Method}\label{redux}

The Amiga Halo Finder identifies all of the halos in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe. \citep{Knebe2001,Knollmann2009,Gill2004} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH. For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.

EDIT: Include specs: mass, formation z, N (just for primary halos? Ask Kelly what she means.)

>>>>

% #####################################
% ############# ABSTRACT ##############
% #####################################

@@

Using cosmological hydrodynamic simulations of Milky Way-type (MW-type) Galaxies, we explore how varying assembly histories affect the mass budget of the SMBH. We examine two MW-mass halos with differing merger histories. One is characterized by several major mergers and the other with a quiescent history. We attempt to identify the importance of merger history on black hole accretion using varying resolution and SPH codes. This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo. In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system. A quiescent galaxy, however, will have a SMBH that mirrors its host's composition. Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history. In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy. Our results imply that galaxy mergers play an important role in the feeding of the SMBHs in the class of Milky Way-type galaxies.

\end{abstract}
\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others}

% ########## END OF ABSTRACT ##########
% #####################################

% #####################################
% ########## INTRODUCTION #############
% #####################################

@@

%[Note to self: Cite one canonical person but also more junior people in the field.]
%\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
 %\S\ref{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep{Kormendy2013}. In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Alexander2005,Papovich2006,Volonteri2012}. The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}.

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000}. A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013}. Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011}. However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}. One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep{DiMatteo2005,Shen2008}. Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy.

@@

% For thesis: M-sigma plot:
%\begin{figure}
%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
%\caption[M-$\sigma$ Relation]{The M-$\sigma$ relatpion which depicts the strong correlation between the mass of a central SMBH and the velocity dispersion of its host's stellar population \citep{Xiao2011}.}
%\label{msigma} 
%\end{figure}
% Cite: Xiao

The black hole mass-bulge luminosity relation was implied by the work of \cite{Dressler1988} and first illustrated by \cite{Kormendy1993}. A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the current, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides \citep[e.g.][]{Richards2006,Reddy2008,Hopkins2010}. Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}. Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.

In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}. It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers \citep{Springel2005,Kocevski2011}. Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich. More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.

Smooth accretion, in particular, may play an important role in fueling these low mass galaxies. Halos less than 10$^{11}$ $M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo \citep{Keres2005}. Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy \citep{Brooks2007,Dekel2009,Nelson2013}. In addition, SMBH feedback, the depositing of energy and angular momentum back into the gas resevoir during accretion, also affects the overarching structure of the host galaxy \citep{Governato2009a}. Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs \citep{Kormendy2013}.

It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history. Therefore, we want to understand how these different galaxy evolutionary paths translate into SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself. \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH. Using a similar method as \cite{Bellovary2013}, this work compares the SMBH and galaxy fueling mechanisms between two Milky Way (MW) mass galaxies. MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}. Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.

We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories. Our ``active'' galaxy, h258 (Figure \ref{h258face}), has a history characterized by major mergers, while our ``quiet'' galaxy, h277 (Figure \ref{h277face}), has a quiescent history with only minor mergers. Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them. We will compare the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within these galaxies. By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine how SMBHs grow in galaxies like our own.

% ####### END OF INTRODUCTION #########
% #####################################

% #####################################
% ####### SIMULATION PARAMETERS #######
% #####################################

\section{Simulation Parameters}\label{sec-model}

% [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)

The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.

An initial DM-only, uniform resolution 50 comoving Mpc box determined which halos would be selected for zoom-in examination, including the two halos examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively. The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively. A recent major merger characterizes the h258 halo at z=1, while h277 has its last significant merger near z $\sim$ 3. A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution. The Gasoline and ChaNGA simulations were run from z=99 to z=0 and z=150 to z=0, respectively.

Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals. The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (1.0 and 10.0 amu cm$^{-3}$ for Gasoline and ChaNGa, respectively; T \textless 10$^4$ K, for both simulations), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1. Star particles form along the Kroupa initial mass function \citep{Kroupa2001}. Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation. SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities. Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}. A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}. Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}. Given the strict adherence of these simulated galaxies with observations, we are confident that they reasonably represent growth in the galaxy and its SMBH. We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.

Since there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent with several theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}. While this method allows the BH formation process to remain physically motivated, BH seeds form if their parent gas particle matches the criteria required for star formation and also maintains zero metallicity (2.5 amu cm$^{-3}$; T \textless 10$^4$ K; Z = 0) \citep{Stinson2006}. A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation fraction of BH seeds at z $\sim$ 3 \citep{Volonteri2008}.

The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. BH formation is dependent only on local environment, neglecting any large-scale properties of the host halo. Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy. Nevertheless, BHs remain near their host centers by choosing dark matter particle masses in high-resolution regions to be on the same order as gas particle masses, minimizing two-body interactions \citep{Bellovary2011}.

Black hole mergers occur when they are separated by less than twice the softening length, and must be bound or satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via merger, black holes gain mass through Bondi-Hoyle gas accretion:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}
where $\alpha$ is a constant equal to 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas. Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively. This energy is distributed as thermal energy to the 32 nearest particles via a kernal probability function. Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations. However, as our main concern is in the relative proportion of gas in various phases, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.

@@

Our low resolution simulations were run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively. Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications. For example, \cite{Governato2009} studied the regrowth of the large disk structure in h258 after its major merger.

@@

To determine whether our results are biased due to low resolution, we created a high resolution version of h258 with the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$. Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$. Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total. The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.  At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.

This volume was run using Charm N-body GrAvity solver, ChaNGa, which scales better and includes a new improved SPH formalism \citep{Keller2014}. The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}. Adjusting the force expression diminishes tensions in the numerical surface due to shear flows, such as Kelvin-Helmholtz instabilities. We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.

@@

% ### END OF SIMULATION PARAMETERS ####
% #####################################

% #####################################
% ######### REDUCTION METHOD ##########	
% #####################################

\section{Reduction Method}\label{redux}

The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}. We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH. For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
